Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-09-01 manuscript/supplemental_material.Rnw
add placenta classification table

@@

  \begin{tabular}{c >{\raggedright}p{1.5in} c >{\raggedright\arraybackslash}p{2in} c}

>>>>

\subsection{Placental Classification}

\begin{table}[hb]
<<placental_classification,echo=FALSE,results="asis">>=
placental.classification <- fread("../data/placental_classification.txt")
print(xtable(placental.classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )

@ 
\caption{Classification of Placenta shapes}
\label{tab:placental_classification}
\end{table}

@@

  \begin{tabular}{c >{\raggedright}p{1.2in} c >{\raggedright\arraybackslash}p{1.8in} c}
